### 2015-07-10 narrative/proposed-work.tex
fixed a few thing in the proposed work.

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layers} needs to be
established so science can be done on the exascale systems in a more efficient manner. Without
predictable performance, not only can the runs be slowed down because of contentions \cite{liu_hotstorage}, 
but also it affects key science decisions, e.g., how much data reduction should be performed.
It is clear that if a run is expected to be slow, an aggresive data reduction needs to be performed
so that science can be done in a timely fashion, which has been reflected in the XGC run (\S~\ref{sec:introduction})
the PI recently participated.

We aim to alleviate the need for the ``magic'' and ``tricks''
that are currently required to optimize application I/O performance
on today's file systems. To accomplish this, we will provide a systematic
approach for describing intentions and other knowledge from {\it user}
space, as well as hidden knowledge of the underlying storage layers.
%For example, ADIOS contains most of the ``best practices'' for I/O optimizations for
%   each file system, and as users place more knowledge into ADIOS, ADIOS
%   can make optimizations.
By capturing user intentions and acting upon them in the middleware, we
free the user from polluting application code with system specific
optimizations which may provide better performance in the short term,
but are detrimental to the long-term maintainability of applications, and
are more sensitive to changes to system configuration. We have successfully
employed this strategy of separation of concerns in ADIOS, and believe that
it will become increasingly important as users want to describe more about
the storage hierarchy and the priorities of different chunks of data. 
Our research is aimed to allow users to simply describe these things and
utilize the descriptions so that the best optimizations can be made.

>>>>

\underline{Principle 2}: {\bf Predictable performance and quality of data in the SSIO layers} needs to be
established so science can be done on the exascale systems in a more efficient manner. Without
predictable performance, not only can the runs be slowed down because of contentions \cite{liu_hotstorage}, 
but also it affects key science decisions, e.g., how much data reduction should be performed.
It is clear that if a run is expected to be slow, an aggresive data reduction needs to be performed
so that science can be done in a timely fashion, which has been reflected in the XGC run (\S~\ref{sec:introduction})
that the PI recently participated.

We aim to alleviate the need for the ``magic'' and ``tricks''
that are currently required to optimize application I/O performance
on today's file systems. To accomplish this, we will provide a systematic
approach for describing intentions and other knowledge from {\it user}
space, as well as allow performance estimations and guarantees 
from the underlyingree storage.
%For example, ADIOS contains most of the ``best practices'' for I/O optimizations for
%   each file system, and as users place more knowledge into ADIOS, ADIOS
%   can make optimizations.
By capturing user intentions and acting upon them in the middleware, we
free the user from polluting application code with system specific
optimizations which may provide better performance in the short term,
but are detrimental to the long-term maintainability of applications, and
are more sensitive to changes to system configuration. We have successfully
employed this strategy of separation of concerns in ADIOS, and believe that
it will become increasingly important because saving all data may not be possible, and
users want the ability to describe and prioritize different chunks of data. 
Our research is aimed to allow users to provide simple descriptions of their data,
which further allows the middleware and storage to optimize application I/O performance.
